Gaussian variance estimation in simulated data sets

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

This script implements the "Gaussian variance estimation" simulation
experiments in the paper. In particular, we compare the Mean Field
Variational Bayes (MFVB) method against SMASH in two scenarios.

The figure and table generated at the end of this script should
match up with the figure and table shown in the paper.

@@

In the first scenario, we simulate data sets with unevenly spaced data
points, and assesse accuracy by computing the mean of the squared
errors (MSE) evaluated at 201 equally spaced points.

@@

```{r simulation-1-main-loop, eval=FALSE} 
cat(sprintf("Running %d simulations: ",nsim1))
for (j in 1:nsim1) {
  cat(sprintf("%d ",j))

@@

  mse.mu.uneven.s8[j]<-mean((mu.est.inter-fTrue(xgOrig))^2)
  mse.sd.uneven.s8[j]<-mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
}
cat("\n")
```

@@

>>>>

This script implements the "Gaussian variance estimation" simulation
experiments in the paper. In particular, we compare the Mean Field
Variational Bayes (MFVB) method against SMASH in two scenarios. The
figure and table generated at the end of this script should match up
with the figure and table shown in the paper.

@@

In the first scenario, we simulate data sets with 500 unevenly spaced data
points, and assess accuracy by computing the mean of the squared
errors (MSE) evaluated at 201 equally spaced points.

@@

```{r simulation-1-main-loop} 
cat(sprintf("Running %d simulations: ",nsim1))
for (j in 1:nsim1) {
  cat(sprintf("%d ",j))

@@

  mse.mu.uneven.smash[j] <- mean((mu.est.inter-fTrue(xgOrig))^2)
  mse.sd.uneven.smash[j] <-
    mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
}
cat("\n")
```

@@

In this scenario, we simulated evenly spaced data points.
